Tables

### 2018-11-05 code/tables.rmd
Cleaned up Table 1

##Heterogeneity may increase with effect size
```{r effect-size-heterogeneity-table}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")

@@

diff_row <- data.frame(rel = "SD observed effect sizes", X1 = sd(rooted_relabilities$X1), X2 = sd(rooted_relabilities$X2), X3 = sd(rooted_relabilities$X3))

het_demo <- rbind(rooted_relabilities, diff_row)

het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "$\\rho$ = 0", "$\\rho$ = .3", "$\\rho$ = .5"), escape = FALSE, digits = 2) %>% 
  kable_styling(position = "left") %>% 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$. SD = standard deviation. Code to reproduce table: osf.io/kf6pt/") %>% 
  row_spec(3, hline_after = T)

@@

##Summary table
```{r data-summary-table}
#library(dplyr)
#library(kableExtra)

@@

##Heterogeneity in preregistered multi-lab psychology studies
```{r heterogeneity-table}
#library(kableExtra)

>>>>

##Table 1
###Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
```{r effect-size-heterogeneity-table}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")

@@

rooted_relabilities %>% knitr::kable("latex", booktabs = T, col.names = c("", "$\\rho_{xy}$ = 0", "$\\rho_{xy}$ = .3", "$\\rho_{xy}$ = .5"), escape = FALSE, digits = 2) %>% 
  kable_styling(position = "left") %>% 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho_{xy}$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$. Code to reproduce table: osf.io/kf6pt/") %>% 
  row_spec(3, hline_after = T)

@@

##Table 2
###Pre-registered multi-lab replication projects
```{r data-summary-table}
#library(dplyr)
#library(kableExtra)

@@

##Table 3
###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity
```{r heterogeneity-table}
#library(kableExtra)
